A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-05-03 04-related.tex
Adicionado Acknowledgments (grant da viagem).

In most synchronous languages, the behavior of external and internal events is
equivalent.
However, in \CEU, internal events introduce stack-based micro reactions within
external reactions, providing more fine-grained control for intra-reaction
execution.
%
This allows for memory-bounded subroutines that can execute multiple times
during the same external reaction.
%
The synchronous languages Statecharts~\cite{statecharts.variants} and
Statemate~\cite{statecharts.statemate} also distinguish internal from external
events.
In the former, \emph{``reactions to external and internal events (...) can be
sensed only after completion of the step''}.
In the latter, \emph{``the receiving state (of the internal event) acts here as
a function''}.
Although the descriptions suggest a stack-based semantics, we are not aware of
formalizations for these ideas for a deeper comparison with \CEU.

@@

Regarding the integration with $C$ language-based environments, \CEU
supports a finalization mechanism for external resources.
%
In addition, \CEU also tracks pointers representing resources that cross $C$
boundaries and forces the programmer to provide associated finalizers.
%
As far as we know, this extra safety level is unique to \CEU among synchronous
languages.

>>>>

In most synchronous languages, the behavior of external and internal events is
equivalent.
However, in \CEU, internal events introduce stack-based micro reactions within
external reactions, providing more fine-grained control for intra-reaction
execution.
%
This allows for memory-bounded subroutines that can execute multiple times
during the same external reaction.
%
The synchronous languages Statecharts~\cite{statecharts.variants} and
Statemate~\cite{statecharts.statemate} also distinguish internal from external
events.
% TODO-FULL
%In the former, \emph{``reactions to external and internal events (...) can be
%sensed only after completion of the step''}.
%In the latter, \emph{``the receiving state (of the internal event) acts here as
%a function''}.
Although the descriptions suggest a stack-based semantics, we are not aware of
formalizations or more precision for a deeper comparison with \CEU.

@@

% TODO-FULL
Regarding the integration with $C$ language-based environments, \CEU
supports a finalization mechanism for external resources.
%
In addition, \CEU also tracks pointers representing resources that cross $C$
boundaries and forces the programmer to provide associated finalizers.
%
As far as we know, this extra safety level is unique to \CEU among synchronous
languages.
